A Global Picture of Food Insecurity and Hunger

### 2020-09-17 docs/modeling_fies.tex
some comments on the supp info in model section

WE NEED HERE A SHORT PARAGRAPH ON HOW RF MODELS WORK, THIS WILL HELP: https://www.kdnuggets.com/2017/10/random-forests-explained.html

@@

To ensure that predicted rates are bounded by 0 and 1 we conduct a logit transformation of the dependent variable and inverse logit transformation of the predictions.

>>>>

WE NEED HERE A SHORT PARAGRAPH ON HOW RF MODELS WORK, THIS WILL HELP: https://www.kdnuggets.com/2017/10/random-forests-explained.html
INCLUDE BAGGING AND RANDOM FEATURE SELECTION, NECESSARY TO EXPLAIN OOB ERROR

@@

STEP-BY-STEP: LOGIT TRANSFORM, TUNE, MODEL, PREDICT, VALIDATE

To ensure that predicted rates are bounded by 0 and 1 we conduct a logit transformation of the dependent variable and inverse logit transformation of the predictions. 
MAYBE STATE THIS SOMEWHERE ELSE, NOT SURE WHERE
